Modelling circumstellar discs with 3D radiation hydrodynamics

### 2009-06-24 SPH-Torus-paper1/sphtorus_benchmark.tex
Add plots of fractional temperature in the disc mid-plane.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@1972 25464f21-6099-402c-b30a-640f1d40d38b

>>>>

To allow a more quantitative comparison the fractional difference in
mid-plane temperature, compared with the results of
\cite{pascucci_2004}, is plotted in
Fig.~\ref{fig:n_part_tem_diff_midpane}.
\begin{figure*}
  \subfigure[$10^5$ particles]{\includegraphics[scale=0.3]{figures/mp_comp1}}
  \subfigure[$10^6$ particles]{\includegraphics[scale=0.3]{figures/mp_comp2}}
  \subfigure[$10^7$ particles]{\includegraphics[scale=0.3]{figures/mp_comp3}}
  \subfigure[$10^8$ particles]{\includegraphics[scale=0.3]{figures/mp_comp4}}
  \caption{Fractional temperature error in the mid-plane for discs represented by
    different numbers of SPH particles.} 
  \label{fig:n_part_tem_diff_midpane}
\end{figure*}
In each case the particles are binned into 1~AU bins and the particle
closest to the mid-plane in that bin is found. The mid-plane
temperature from \cite{pascucci_2004} is linearly interpolated to the
cyclindrical radius of the particle and the fractional temperature
error is calculated.
